Microplastics in the Urban Environment

### 2021-10-08 code/analysis_code/exploration.Rmd
final updates project pt2

mpdata %>% ggplot(aes(x = date, y = particles_l)) + geom_boxplot(aes()) + labs(title = "Microplastic Concentration")

@@

# MP level vs population
```{r}
mpdata %>% ggplot(aes(x = population, y = particles_l)) + geom_point()
```

@@

# try plot again
```{r}
mpdata %>% ggplot(aes(x = e.coli.cfu, y = particles_l)) + geom_point() + theme(axis.text.x = element_text(angle = 90, hjust=1))
```

@@

```{r}
mpdata %>% ggplot(aes(x = e.coli.cfu, y = particles_l)) + geom_point() + theme(axis.text.x = element_text(angle = 90, hjust=1)) + scale_x_continuous(trans='log10') +
  scale_y_continuous(trans='log10')
```

@@

```{r}
mpdata %>% filter(particles_l < 400) %>% ggplot(aes(x = particles_l)) + geom_histogram()
```

@@

```{r}
summary(mpdata$particles_l)
```

>>>>

p1 <- mpdata %>% ggplot(aes(x = date, y = particles_l)) + geom_boxplot(aes()) + labs(title = "Microplastic Concentration")

plot(p1)

#save figure
figure_file = here("results","concentrationbydate.png")
ggsave(filename = figure_file, plot=p1)
```

@@

# MP level vs population
```{r}
p2 <- mpdata %>% ggplot(aes(x = population, y = particles_l)) + geom_point()

plot(p2)

#save figure
figure_file = here("results","particlesvpop.png")
ggsave(filename = figure_file, plot=p1)
```

@@

# try plot again
```{r}
p3 <- mpdata %>% ggplot(aes(x = e.coli.cfu, y = particles_l)) + geom_point() + theme(axis.text.x = element_text(angle = 90, hjust=1))

plot(p3)

#save figure
figure_file = here("results","mpvbacteria.png")
ggsave(filename = figure_file, plot=p3)
```

@@

```{r}
p4 <- mpdata %>% ggplot(aes(x = e.coli.cfu, y = particles_l)) + geom_point() + theme(axis.text.x = element_text(angle = 90, hjust=1)) + scale_x_continuous(trans='log10') +
  scale_y_continuous(trans='log10')

plot(p4)

#save figure
figure_file = here("results","logmpvbacteria.png")
ggsave(filename = figure_file, plot=p4)
```

@@

```{r}
p5 <- mpdata %>% filter(particles_l < 400) %>% ggplot(aes(x = particles_l)) + geom_histogram()

plot(p5)

#save figure
figure_file = here("results","distribution.png")
ggsave(filename = figure_file, plot=p5)
```

@@

```{r}
summary(mpdata$particles_l)

### 2021-10-08 products/manuscript/Manuscript.Rmd
final updates project pt2

## Description of data and data source
_Describe what the data is, what it contains, where it is from, etc. Eventually this might be part of a methods section._

## Questions/Hypotheses to be addressed
_State the research questions you plan to answer with this analysis._

@@

@@

@@

_Use a combination of text/tables/figures to explore and describe your data. You should produce plots or tables or other summary quantities for the most interesting/important quantities in your data. Depending on the total number of variables in your dataset, explore all or some of the others. FIgures produced here might be histograms or density plots, correlation plots, etc. Tables might summarize your data._

>>>>

## Description of data and data source

The data that I am using for this project is from my personal undergraduate research project on freshwater microplastics in Athens, GA. The study is ongoing and was conducted in collaboration with the Upper Oconee Watershed Network (UOWN) via their quarterly sampling events. There is one year’s worth of quarterly data, with the following sample dates: November 2020, February 2021, April 2021, and July 2021. The data include variables such as sample site, latitude and longitude, watershed location, and duplicate A and B counts of microplastics observed per filter. For the most recent sampling date, July 2021, there is additional data where a second counting session was performed, in order to assess the comparability of parallel counts. There are about 136 observations of ~10 variables in total in the dataset. The independent variables – site location, coordinates, watershed location, etc – were retrieved from UOWN. Values for microplastic counts were recorded based on visual identification via a dissecting microscope, performed by myself and by a small team of <10 volunteers.

Additional data [write up further explanation]:
 - small area population via census zipcode
 - UOWN bacteria level data
 - local land cover
 - distance from water reclamation facility (WRF)

## Questions/Hypotheses to be addressed
The questions that I want to answer with this data include the following:
 - Can we characterize microplastics in Athens, GA using a citizen science approach? 
 -	What are the levels of microplastics like in Athens, GA overall? 
 -	How do microplastic levels differ based on location within the region?

Questions that I want to answer that will require gathering more data using coordinates/watershed info include:
 -	Is microplastic concentration impacted by local land use? 
 -	Is microplastic concentration impacted by localized population levels in specific neighborhoods?
 -	Does wastewater treatment plant effluent from nearby facilities increase microplastic concentration at affected sites?
 -	Are microplastic levels correlated to bacteria levels measured at the same sites? 
These questions also relate to hypothesized predictors of microplastic pollution: population level, land use, wastewater treatment plant effluent, and microbial water quality.

My ideas for how to analyze this data include using non-parametric statistical tests, correlation matrices, and modeling (?) to characterize and compare observations.

@@

- Methods for sample collection and processing for UOWN MP water samples

@@

Since I am performing importing and cleaning in a separate document, in this section I will provide an overview of my steps/methods for wrangling the data, without actual code in this section.

Import of additional data
 - census - American Community Survey
 - NGIS land cover
 - zip code - Bing reverse geocoding
 - WRF locations: located on Google Maps, coordinates recorded in Excel spreadsheet
 - UOWN bacteria data (citation/attribution available on UOWN.org)

@@

This section will contain the key products of my exploratory analysis (located in exploration.Rmd) when complete. Since I am keeping this document in manuscript style, I will keep processing/exploration/analysis code separate. 
_Use a combination of text/tables/figures to explore and describe your data. You should produce plots or tables or other summary quantities for the most interesting/important quantities in your data. Depending on the total number of variables in your dataset, explore all or some of the others. FIgures produced here might be histograms or density plots, correlation plots, etc. Tables might summarize your data._
